### 2022-01-17 response2/response2.tex
Finalize res to q2

\subsection*{General changes to the manuscript}

We have made some minor changes in language and presentation to improve the clarity and organization of the manuscript.
\begin{itemize}
    \item Section I - seventh paragraph (page 2): \\
        {\color{Red} In Sec. VII, we discuss the physical significance of our theoretical results and their possible use in future nanoelectronic devices.
        Finally, we summarize our findings and present our conclusions in Sec. VIII.}
\end{itemize}

@@

>>>>

@@

\subsubsection*{Comment 2 -
\color{RoyalBlue} Moreover, the authors are misinterpreting the results of earlier theoretical works. In particular, Ref. [31] demonstrates both the effect of photo excitations of electrons and the dressing of electronic states.}

We thank the reviewer for mention this deficiency. We believe this comment from the reviewer comes mainly from our statement

{\color{CadetBlue} “This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs [54-57]. These formalisms provide a proper explanation for the experimental observations of MIROs. However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) electromagnetic fields.
In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (nonabsorbable) field.
The influence induced by a pure dressing field on
magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.”}

in the Section I (page 1 and page 2) in the manuscript. It is important to note that the Ref. [31] in our previous response to reviewer comments represents the the
following study:

\textit{I. A. Dmitriev, M. Khodas, A. D. Mirlin, D. G. Polyakov, and M. G. Vavilov, Phys. Rev. B 80, 165327 (2009).}

In our previous manuscript we have represented it as Ref. [57]. In the present response we refer it as \cite{dmitriev09}.
On a re-reading the previous manuscript, we see that the language we had used here is ambiguous and admit that the statement gives a meaning that is quite different to what we were trying to convey.

What we meant to say here is that, work presented in Dmitriev \textit{et al.} \cite{dmitriev09} related to the microwave induced resistance oscillations (MIROs) which can be observed in 2DEG subjected to both magnetic field and low-frequency (microwave) radiation. As mentioned by the reviewer, Ref. \cite{dmitriev09} have properly described the magnto-trasnport properties using the dressed states of electrons as well as the photon interactions. On the other hand, if the driving field is in high-frequency regime, we can neglect the photon interactions as mentioned in the response to the first comment. In addition, we can identify that the high-frequency and low-frequency radiation lead to two different behaviors of the magnto-trasnport characteristics of dressed quantum Hall systems \cite{dini16}. With the low-frequency illumination, particular effects can be observed known as ``zero resistance states" where we can observe increased longitudinal conductivity. However, under high-frequency radiation decrease both the broadening of Landau levels and the longitudinal conductivity.
Our analysis is focused on high-frequency regime where we can significantly suppress the photon interactions in the Floquet system. Therefore, we meant to mention this difference between the our study and the Ref. \cite{dmitriev09}. We never meant to say that Dmitriev \textit{et al.} \cite{dmitriev09} only consider the effects of photon excitations.

To incorporate your comment to the manuscript, we removed the above mentioned statement and replaced it with wording which hopefully would convey our meaning better.

\begin{itemize}
  \item Section I - second paragraph (page 5):\\
  {\color{Red}
  This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}. These formalisms provide a proper explanation for the experimental observations of MIROs. However, these experimental and theoretical works have been linked to effects of low-frequency (microwave) electromagnetic fields which results an increase of longitudinal conductivity.
  In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system leads to different behavior that reduce the longitudinal conductivity \cite{dini16}.
  Since high-frequency radiation only contribute to the suppression of electron scattering, the driving field can be treated as a pure dressing (nonabsorbable) field \cite{dini16}.
  Thus, the influence induced by a high-frequency pure dressing field on
  magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
  }
\end{itemize}

In addition, we have made the following minor change in language and presentation to match the rest of the manuscript better to the changes done to address the reviewer’s comments.

\begin{itemize}
  \item Section VI - sixth paragraph (page 9):\\
  {\color{Red}
  However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on low-frequency fields.
  }
  \item Section VI - sixth paragraph (page 9):\\
  {\color{Red} In our case, the applied dressing field is in the high-frequency regime where we can neglect the photon interactions. The only influence of the electromagnetic field is the suppression of electron scattering.}
\end{itemize}
